---
title: "MicData"
author: "Yolanda Yang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MicData}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r}
## Load the MicData package!
library(MicData)
```

## Choose the mic you want!

Now with this package, you can try to get all the mic models by calling ```gModel()```.
This will give you a list of models available. Inside the ```gModel()``` function, a helper function ```getMember()``` is called to get a specific member of each vector in a list.

```{r}
## Let's get all the model name!
gModel()
```

## Get a description!

After you have make your decision, use the model name that you get from ```gModel()``` as the input of ```gDescription()``` to get a general description of that mic! Let's try to get a description of the TLM49 mic by using ```gDescription("tlm49")```. Note if you don't pass any input to ```gDescription()```, the default input is ```"u87"``` which gets you the description of the widely recognized u87 mic~! There are special cases that a number of models sharing one common url. Special case handling involves url redirecting and retrieving a common description from the common url.

```{r}
## Get the description of TLM49!
gDescription("tlm49")
```

## Please tell me the technical data!

You decided that you like this mic very much according to its description. Why not have a look at its technical data before you buy it? Again, use the model name that you get from ```gModel()``` as the input of ```gMicData()``` to get the technical data of your favorite mic! To me, the KU100 binaural mic seems to be very interesting! ```gMicData("ku100")``` would give me what I want! Note if you don't pass any input to ```gMicData()```, the default input is ```"u87"``` which gets you the technical data of the widely recognized u87 mic~! There are special cases that a number of models sharing one common url. Special case handling involves url redirecting and retrieving the technical data of multiple models from the common url.


```{r, results='asis'}
## Get the techinical data of KU100!
knitr::kable(gMicData("ku100"))
```

## Reflections

Everything worked nicely until I got to the point to do a ```devtools::check()```. I could not get ```devtools::check()``` completed at first because the url I used originally was a secure site that begins with ```https://``` instead of ```http://``` and ```readLines()``` could not access the server easily when doing such a check. ```getURL()``` in 'RCurl" package seems to be the solution, but in that case all the html syntax and useful data would clump together into several character strings instead of separating into lines. I would have to think of another way to extract the data, which I don't have any idea how to do that.. Function ```htmlTreeParse()``` in "XML" package also seems to be useful to parse the html syntax. However, I was stuck on how to deal with the parsed object after applying ```htmlTreeParse()``` as I am not familiar with html format at all. Then, I tried to change ```https://``` to ```http://``` and luckily, it worked! Now I can run a ```check()``` without getting any error! However, I still don't have any clue on how to deal with the problem if the url really begins with ```https://```. Any thoughts would be appreciated! =)
